SAT Solving for Vesicle Traffic Systems in Cells

### 2017-07-20 paper/experiments.tex

% C_es :Self edges are allowed
% C_ed : Every edge is distinct 
  \end{tabular}
\caption{{\bf Activity regulation of molecules vs. graph connectivity.}}
\label{tab:grph}
\vspace{-5ex}
\end{table}

@@

In Table~\ref{tab:qf-grabh}, we present the running times for the search of
VTSs of sizes 2 to 10 that satisfy the variants.
%
The experiments were done on a machine with Intel(R) Core(TM) i3-4030U
CPU @ 1.90GHz processor and 4GB RAM.
%
We have compared our performance with the performance of our earlier 
CBMC based implementation.
%
For example, the formula for variation F, the total number of
compartments ($|N|$) equals to 10, returns in 129.78 minutes (7786.8 secs)
with a SAT result.
%
In comparison, CBMC results in OUT OF MEMORY for $|N|$ greater than 5.
%
``!'' indicate that the constraints were unsatisfiable.
%
Hence with the use of this novel encoding, we are able to scale the
system to a much larger compartmentalized system, especially to
eukaryotic cells with a total number of 10 compartments. \textbf{Not only we have improved finding a SAT model but this encoding also did better in comparison to cbmc in the
case of refutation that no model exists. Refer table variant A timing
comparison and VARIANT D with N =2.}
%
% \ankit{
% This additional scalability can provide us leverage to ask for related
% open questions that were not previously possible, for example, what is
% the minimum number of molecules required to satisfy the vesicular
% traffic system in eukaryotes.}
%
Furthermore, we experimented with limits of our tools and found
that $\zthree$ was able to solve the constraints up to $\sim{14-18}$ nodes.

% \vspace{-3ex}

>>>>

% C_es :Self edges are allowed
% C_ed : Every edge is distinct 
  \end{tabular}
\caption{{\bf Activity regulation of molecules vs. graph connectivity.}}
\label{tab:grph}
\end{table}

@@

In Table~\ref{tab:qf-grabh}, we present the running times for the search of
VTSs of sizes 2 to 10 that satisfy the variants.
%
The experiments were done on a machine with Intel(R) Core(TM) i3-4030U
CPU @ 1.90GHz processor and 4GB RAM.
%
We have compared our performance with the performance of our earlier 
CBMC based implementation (O'cbmc).
%
For example, the formula for variation F, the total number of
compartments ($|N|$) equals to 10, returns in 129.78 minutes (7786.8 secs)
with a SAT result.
%
In comparison, CBMC results in OUT OF MEMORY for $|N|$ greater than 5.
%
``!'' indicate that the constraints were unsatisfiable.
%
 \textbf{Using this encoding in comparison to the old one, not only we got efficiency improved for finding a SAT model but also did better in the case of refutation that no model exist (Table 2 variant A timing comparison and variant D with N =2).}. Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to
eukaryotic cells with a total number of 10 compartments.
%
% \ankit{
% This additional scalability can provide us leverage to ask for related
% open questions that were not previously possible, for example, what is
% the minimum number of molecules required to satisfy the vesicular
% traffic system in eukaryotes.}
%
Furthermore, we experimented with limits of our tools and found
that $\zthree$ was able to solve the constraints up to $\sim{14-18}$ nodes.
